\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 bmc.tex
.

% include an algorithm
We now describe the entire procedure in three steps.
\begin{enumerate}
    \item Given a black box system $\System$ specified by
        $\simulate^\System$, we
        use scatter-and-simulate with ($\Delta$-length) trajectory
        segments to sample a finite reachability graph
        $\scr{H}(\Delta)$.
    \item Using regression, we enrich the graph relations and annotate
        the edges with the estimated affine maps.
    \item Interpreting the directed reachability graph as a transition
        system, we use a bounded model checker to find fixed length
        violations to safety properties.
\end{enumerate}

@@

We now describe the above using the Van der Pol oscillator benchmark
presented in \cite{zutshi2014multiple}. Simulations generated using
uniformly random samples are shown in \figref{vdp-cont}. We want to
check the property $P_3$, indicated by the red box, given the initial
set indicated by the green box. The abstraction is defined by
$\quant_{0.2}(\x)$, which results in an evenly gridded state-space,
where each cell is of size $0.2 \times 0.2$ units.
Scatter-and-simulate is then used to construct the abstract graph $G$,
using $2$ samples per cell and the time step $\Delta = 0.1s$. The
complete process follows.

\begin{enumerate}
    \item{\emph{Abstract}} Consider an implicit abstraction induced by the quantization
    function $\quant_\epsilon(\x)$. The corresponding reachability
    graph $\scr{H}(\Delta)$ (with time step $\Delta$) is given by
    $\tupleof{\scr{C},\areach{\Delta}, \scr{C}_0, \scr{C}_u}$.
\item{\emph{Discover}}: Using scatter-and-simulate, enumerate a finite number
    of cells (vertices) and the relations (edges) of the graph
    $\scr{H}(\Delta)$. Associate the set of generated trajectory
    segments with their respective originating cells using a map $D:C
    \mapsto \setof{\pi | start(\pi) \in C}$. The discovered
    abstraction is show in \figref{vdp-abs}. As mentioned, red cells
    are unsafe and green cells are initial cells.
\item{\emph{Relationalize}} For each cell $C$, perform regression analysis on
    the respective set of trajectory segments $D(C)$, and compute a
    set of affine relations $R_{C,C'}(\x,\x')$ between $\x \in C$ and $\x'
    \in C'$ s.t., $\text{edge} (C,C') \in \scr{H}(\Delta)$. Annotate
    each edge in the graph $\scr{H}(\Delta)$ with the respective
    relation.

@@

\item{\emph{Model Check}} The graph $\scr{H}(\Delta)$ can now be viewed as a
    transition system $\tupleof{C,\x,\scrT,C_0,\HybridStates_0}$,
    where $C \in vertices(\scr{H}(\Delta))$ and $\x \in
    \HybridStates$. A transition $\tau \in \scrT$ is of the form
    $\tupleof{C, C',\rho_{\tau}}$, where $\rho_{\tau}(\x,\x')
    \subseteq \setof{R_{(C,C')}(\x,\x') |( C,C') \in
    edge(\scr{H}(\Delta))}$.
\item{\emph{Check Counter-example}} The infinite state (but finite location) transition system can
    be model checked to find a concrete counter-example, which if
    exists, can indicate the existence of a similar trace in the
    original black-box system $\System$. The latter check is carried
    out as before, using the numerical simulation function
    $\simulate$. For the given example, the model checker is unable to
    find a counter-example.
\end{enumerate}

\inclfig[width=0.75\linewidth]{vdp_cont_traces.png}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.75\linewidth]{vdp_abs.png}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=\linewidth]{vdp_disc_map.png}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.40\linewidth]{vdp_graph.png}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}

>>>>

\section{Model Checking}

As a final step, the enriched graph is model checked for the given
safety property. If a counter-example is found, it is simulated using
the $\simulate$ function and if reproducible, a violation is
concluded. In all other cases the falsification results in an
`unknown' result.

% % include an algorithm
% We now describe the entire procedure in three steps.
% \begin{enumerate}
%     \item Given a black box system $\System$ specified by
%         $\simulate^\System$, we
%         use scatter-and-simulate with ($\Delta$-length) trajectory
%         segments to sample a finite reachability graph
%         $\scr{H}(\Delta)$.
%     \item Using regression, we enrich the graph relations and annotate
%         the edges with the estimated affine maps.
%     \item Interpreting the directed reachability graph as a transition
%         system, we use a bounded model checker to find fixed length
%         violations to safety properties.
% \end{enumerate}

@@

We now describe the pesented technique using the Van der Pol
oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
generated using uniformly random samples are shown in
\figref{vdp-cont}. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. The
abstraction is defined by $\quant_{0.2}(\x)$, which results in an
evenly gridded state-space, where each cell is of size $0.2 \times
0.2$ units.  Scatter-and-simulate is then used to construct the
abstract graph $G$, using $2$ samples per cell and the time step
$\Delta = 0.1s$. The complete process follows.

\begin{enumerate}
    \item{\emph{Abstract}}: Assume an implicit abstraction using the quantization
        function $\quant_{\epsilon=0.2}(\x)$. The corresponding reachability
    graph is $\scr{H}(\Delta=0.1)$.
\item{\emph{Discover}}: Using scatter-and-simulate, enumerate a finite number
    of cells (vertices) and the relations (edges) of the graph
    $\scr{H}(0.1)$. Associate the set of generated trajectory
    segments with their respective originating cells using a map $\ds:C
        \mapsto \setof{(\vx,\vx') |\vx \in C}$. The discovered
    abstraction is show in \figref{vdp-abs}. The red cells
    are unsafe and green cells are initial cells.
\item{\emph{Relationalize}}: For each cell $C$, perform regression analysis on
    the respective set of trajectory segments $D(C)$, and compute a
    set of affine relations $R_{C,C'}(\x,\x')$ between $\x \in C$ and $\x'
    \in C'$ s.t., $\text{edge} (C,C') \in \scr{H}(0.1)$. Annotate
    each edge in the graph $\scr{H}(0.1)$ with the respective
    relation.

@@

\item{\emph{Model Check}}: The graph $\scr{H}(0.1)$ can now be viewed as a
    transition system $\tupleof{C,\x,\scrT,C_0,\HybridStates_0}$,
    where $C \in vertices(\scr{H}(0.1))$ and $\x \in
    \HybridStates$. A transition $\tau \in \scrT$ is of the form
    $\tupleof{C, C',\rho_{\tau}}$, where $\rho_{\tau}(\x,\x')
    \subseteq \setof{R_{(C,C')}(\x,\x') |( C,C') \in
    edge(\scr{H}(0.1))}$.
\item{\emph{Check Counter-example}}: The infinite state (but finite location) transition system can
    be model checked to find a concrete counter-example, which if
    exists, can indicate the existence of a similar trace in the
    original black-box system $\System$. The latter check is carried
    out as before, using the numerical simulation function
    $\simulate$. For the given example, the model checker is unable to
    find a counter-example.
\end{enumerate}

\inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=0.95\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}
